### 2023-12-27 sections/1-introduction.tex
filled in related works

Recent search algorithms for tackling the exponential growth of data include hierarchical navigable small world networks (HNSW)~\cite{Malkov2016EfficientAR}, InVerted File indexing (FAISS-IVF)~\cite{johnson2019billion}, random projection and tree building (ANNOY)~\cite{annoy}, and entropy-scaling search~\cite{yu2015entropy, ishaq2019clustered}.

@@

TODO: Paragraph summarizing HNSW.

@@

TODO: Paragraph summarizing FAISS-IVF.

@@

TODO: Paragraph summarizing ANNOY.

>>>>

Recent search algorithms for tackling the exponential growth of data include hierarchical navigable small world networks (HNSW)~\cite{Malkov2016EfficientAR}, InVerted File indexing (FAISS-IVF)~\cite{faissivf}, random projection and tree building (ANNOY)~\cite{annoy}, and entropy-scaling search~\cite{yu2015entropy, ishaq2019clustered}.

@@

HNSW is an approximate $k$-NN search method based on navigable small world (NSW) graphs and skip lists. 
Similar to the NSW algorithm, HNSW builds a graph of the dataset, but unlike NSW, the graph is multi-layered.
The query point and each data point are inserted into the graph one at a time, and, upon insertion, the element is joined by an edge to the $M$ nearest nodes in the in the graph, where $M$ is a tunable parameter. 
The highest layer in which an element can be placed is determined randomly with an exponentially decaying probability distribution.
Search starts at the highest layer and descends to the lowest layer, greedily following a path of edges to the nearest node, until reaching the query point. 
To improve accuracy, the efSearch hyperparameter can be changed to specify the number of closest nearest neighbors to the query vector to be found at each layer.

@@

InVerted File indexing (IVF) is a method for approximate $k$-NN search. 
The dataset is clustered into a high dimensional Voronoi diagram, and whichever cell the query point falls into is then searched exhaustively.
The number of cells created is governed by the $n_{list}$ parameter. 
Increasing this parameter decreases the number of points being exhaustively searched, so it improves speed at the cost of accuracy.
To mitigate accuracy issues caused by a query point falling near a cell boundary, IVF has a tunable parameter $n_{probe}$, which specifies the number of cells to search.

@@

Annoy is an approximate $k$-NN search method based on random projection and tree building.
At each intermediate node of the tree, two points are sampled from the space, and the hyperplane equidistant from them is chosen to divide the space into two subspaces.
This process is repeated multiple times to create a forest of trees, and the number of times the process is repeated is a tunable parameter.
{\color{red} TODO: I'm still unclear what they are doing with these trees.}
